---
title: "Lab 01 - Hello R"
author: "Vanessa Gill"
date: "02/08/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

I would expect 1846 rows and 3 columns.
The variables are dataset, x-values, and y-values.

### Exercise 2

Plot of the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot of the Star dataset:

```{r plot-star, fig.height=5, fig.width=10}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation between 'x' and 'y' in this data set:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Add code and narrative as needed.
Note that two R chunks are given but they are not labeled.
Use the convention from above to name them appropriately.

```{r}

```

```{r}

```

### Exercise 5

Add code and narrative as needed.
To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.
